---
title: "Association Tests Exercises"
output: html_notebook
---

In the previous video, Rafa showed how to calculate a Chi-square test from a table. Here we will show how to generate the table from data which is in the form of a dataframe, so that you can then perform an association test to see if two columns have an enrichment (or depletion) of shared occurences.

Download the assoctest.csv file into your R working directory, and then read it into R:

```{r}
d = read.csv("assoctest.csv")
head(d)
```

Association Tests Exercises #1

Compute the Chi-square test for the association of genotype with case/control status (using the table() function and the chisq.test() function). Examine the table to see if it look enriched for association by eye. What is the X-squared statistic?

```{r}
tab <- table(d$allele, d$case)
tab
```

```{r}
chisq.test(tab)
```

```{r}
chisq.test(tab)$p.value
```
A: 3.3437

Association Tests Exercises #2
Compute the Fisher's exact test ( fisher.test() ) for the same table. What is the p-value?

```{r}
tab = table(d$allele, d$case)

fisher.test(tab)
```

